Kids PM Summary

### 2020-08-26 lrti_tracking.Rmd
fig 1 summary stats

---
title: "Kids LRTI tracking"
author: "Ethan Walker"
date: "Started 6 April 2020, Updated 28 July 2020"
output: pdf_document 
---

@@

write_csv(lrti_final_data, paste0(file_path, "Output/lrti_final_data.csv"), na = "")
```

>>>>

---
title: "Kids LRTI tracking"
author: "Ethan Walker"
date: "Started 6 April 2020, Updated 26 Aug 2020"
output: pdf_document 
---

@@

write_rds(lrti_final_data, paste0(file_path, "Output/lrti_final_data.rds"))
write_csv(lrti_final_data, paste0(file_path, "Output/lrti_final_data.csv"), na = "")
```

# Summary stats for LRTI time at-risk. Check for odd values to finish data cleaning.
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

lrti_final_data <- read_rds(paste0(file_path, "Output/lrti_final_data.rds"))

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  select(area, home_winter_id, treatment_assigned) %>% 
  distinct(area, home_winter_id, .keep_all = TRUE)

summary_stats <- lrti_final_data %>% 
  filter(winter_id != 0) %>% 
  group_by(area, winter_id) %>% 
  summarize("N" = n(),
            "Mean PT Possible" = mean(person_time_possible, na.rm = TRUE),
            "SD PT Possible" = sd(person_time_possible, na.rm = TRUE),
            "Min PT Possible" = min(person_time_possible, na.rm = TRUE),
            "Med PT Possible" = median(person_time_possible, na.rm = TRUE),
            "Max PT Possible" = max(person_time_possible, na.rm = TRUE),
            "Mean PT LRTI" = mean(person_time_lrti_total, na.rm = TRUE),
            "SD PT LRTI" = sd(person_time_lrti_total, na.rm = TRUE),
            "Min PT LRTI" = min(person_time_lrti_total, na.rm = TRUE),
            "Med PT LRTI" = median(person_time_lrti_total, na.rm = TRUE),
            "Max PT LRTI" = max(person_time_lrti_total, na.rm = TRUE))

summary_stats

fig1_stats <- lrti_final_data %>% 
  left_join(health_exposure_data_sampling_day, by = c("area", "home_winter_id")) %>% 
  filter(winter_id != 0) %>% 
  group_by(area, winter_id, treatment_assigned) %>% 
  filter(!is.na(person_time_possible)) %>% 
  mutate(child_weeks_obs = as.numeric(person_time_possible),
         child_weeks_obs = sum(child_weeks_obs)/7) %>% 
  distinct(area, winter_id, treatment_assigned, .keep_all = TRUE) %>% 
  select(area, winter_id, treatment_assigned, child_weeks_obs)

fig1_stats
```

### 2020-08-26 pm_summary.Rmd
fig 1 summary stats

>>>>

# Summary stats for Figure 1
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

exposure_analysis_data_short <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_short.rds")) %>% 
  filter(winter_id == 1) %>% 
  select(area, home_winter_id, winter_id, treatment_assigned, 
         pm_sample_interval, pm_mean_sampling_period) %>% 
  arrange(area, home_winter_id, pm_mean_sampling_period) %>% 
  distinct(area, home_winter_id, .keep_all = TRUE)

fig1_stats <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  group_by(area, winter_id, treatment_assigned) %>% 
  filter(!is.na(pm_sample_interval)) %>% 
  mutate(pm_sample_days = as.numeric(pm_sample_interval),
         pm_sample_days = sum(pm_sample_days)) %>% 
  distinct(area, winter_id, treatment_assigned, .keep_all = TRUE) %>% 
  select(area, winter_id, treatment_assigned, pm_sample_days)

fig1_stats
```
